%Este trabalho está licenciado sob a Licença Atribuição-CompartilhaIgual 4.0 Internacional Creative Commons. Para visualizar uma cópia desta licença, visite http://creativecommons.org/licenses/by-sa/4.0/deed.pt_BR ou mande uma carta para Creative Commons, PO Box 1866, Mountain View, CA 94042, USA.

\documentclass[12pt]{book}

\input ../preambulo.tex

\ifispython
\lstset { %
  language=Python,
}
\fi

\makeindex

\begin{document}

\frontmatter

\title{Redes Neurais Artificiais}
\author{Pedro H A Konzen}
\date{\today}
\ifishtml
\else
\addcontentsline{toc}{chapter}{Capa}
\fi

\maketitle

% \nocite{Goodfellow2016a}

\include{licenca}
\include{prefacio}

\tableofcontents
\addcontentsline{toc}{chapter}{Sumário}

\mainmatter

\include{./cap_intro/cap_intro}
\include{./cap_perceptron/cap_perceptron}
\include{./cap_mlp/cap_mlp}
\include{./cap_pinns/cap_pinns}

%resposta dos exercícios
\ifisbook
\include{./cap_respostas/cap_respostas}
\fi

%references
%references
\ifisbook
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{\bibname}
\fi

\begin{thebibliography}{99}
\bibitem{Agirseven2010a}
  A\u{g}irseven, D., Özi\c{s}, T.. \textit{An analytical study for Fisher type equations by using homotopy   perturbation method}, Computers and Mathematics with Applications, vol. 60, p. 602-609, 2010. \texttt{DOI: \href{http://dx.doi.org/10.1016/j.camwa.2010.05.006}{10.1016/j.camwa.2010.05.006}}

\bibitem{Goodfellow2016a}
  Goodfellow, I., Bengio, Y., Courville, A.. Deep learning, {MIT} Press, Cambridge, {MA}, 2016.

\bibitem{Haykin2005a}
  Neural Networks: A Comprehensive Foundation, Haykin, S.. Pearson:Delhi, 2005. ISBN: \texttt{978-0020327615}.

\bibitem{Raissi}
  Raissi, M., Perdikaris, P., Karniadakis, G.E.. Physics-informed neural networks: A deep learning framework for solving forward and inverse problems involving nonlinear partial differential equations. Journal of Computational Physics 378 (2019), pp. 686-707. DOI: \texttt{10.1016/j.jcp.2018.10.045}.

\bibitem{Mata}
  Mata, F.F., Gijón, A., Molina-Solana, M., Gómez-Romero, J.. Physics-informed neural networks for data-driven simulation: Advantages, limitations, and opportunities. Physica A: Statistical Mechanics and its Applications 610 (2023), pp. 128415. DOI: \texttt{10.1016/j.physa.2022.128415}.

\end{thebibliography}

\end{document}
